Dynamic Topic Modeling for Voice Dialogues

### 2024-05-20 paper/main.tex
udapte experiments

@@

\begin{center}
    \begin{tabular}{ | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{model} & \multicolumn{1}{| c |}{AMI} &  \multicolumn{1}{| c |}{ICSI} \\
        \hline
        pyannote-speaker-diarization-3.1 & 18.5 & 17.38 \\  
        \hline
    \end{tabular}
    \captionof{table}{Speaker diarization evaluation}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \hline
        model & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & 0.446 & 0.458 & 0.378 \\
        TeT + BERT & 0.425 & 0.439 & 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        Our solution BERT-NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        Our solution BERT-CLS & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Text datasets segmentation}
\end{center}

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | } 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{AMI} &  \multicolumn{3}{| c |}{ICSI} \\
        \hline
        model  & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.0641 & 0.762 & 0.730 & 0.109 \\
        GraphSeg & Pk & wd & f1 & Pk & wd & f1 \\
        TextTilling & Pk & wd & f1 & Pk & wd & f1 \\
        TeT + BERT & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        Our solution BERT-NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        Our solution BERT-CLS & Pk & wd & f1 & Pk & wd & f1 \\  
        \hline
    \end{tabular}
    \captionof{table}{Audio datasets segmentation}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \hline
        model & TD & TC & TD & TC  \\ 
        \hline
        LSA  & 0.25824 & 0.00951 & 0.420026 & -0.01929 \\
        BertTopic & 0.34823 & \cellcolor{green!60} 0.02751 & 0.420026 & \cellcolor{green!60} 0.01929 \\
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.80707 & \cellcolor{green!20} 0.01621 & \cellcolor{green!60} 0.49525 & \cellcolor{green!20} 0.005887 \\ 
        Qwen1.5 7B & \cellcolor{green!20} 0.72169  & 0.015453 & \cellcolor{green!20} 0.47777  & -0.07682\\ 
        Mistral 7B & 0.63344 & 0.002248 & 0.34215 & -0.01689 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Text datasets topics extraction}
\end{center}

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{Product} &  \multicolumn{2}{| c |}{Academic} \\
        \hline

        \hline
        LSA & 0.009648 & 0.001375 & 0.013490 & -0.00172 \\ 
        BertTopic & 0.013996 & \cellcolor{green!60} 0.02485 & 0.029090 & \cellcolor{green!60} 0.27210 \\ 
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.50863 & \cellcolor{green!20} 0.11409 & \cellcolor{green!60} 0.76137 & \cellcolor{green!20} 0.14734 \\ 
        Qwen1.5  & \cellcolor{green!20} 0.38641 & 0.10328 & \cellcolor{green!20} 0.7185  & 0.00237\\ 
        Mistral 7B & 0.29852 & 0.084103 & 0.5761 & -0.11318 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Audio datasets topics extraction}
\end{center}

The result of experiments in zero-shot that LlaMA 3 8B demonstrate the best performance, it is far ahead of everyone in Topic Diversity and competes in Topic Coherence with BertTopic. 
A strong drawdown in quality relative to extractive model was also noticed in the article PromptTopic \cite{prompttopic:2023}, where the models also lost to BertTopic in Topic Coherence.

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{AMI} &  \multicolumn{2}{| c |}{ICSI} \\
        \hline
        model & TD & TC & TD & TC  \\ 
        \hline
        LLaMA3 zero-shot & 0.50863 & 0.11409 & 0.76137 & 0.14734 \\ 
        LLaMA3 few-shot & \cellcolor{green!20} 0.51291 & \cellcolor{green!20} 0.12129 & \cellcolor{green!60} 0.78201 & \cellcolor{red!10} 0.13985 \\ 
        \hline
        Qwen1.5 zero-shot & 0.38641 & 0.10328 & 0.7185 & 0.00237 \\ 
        Qwen1.5 few-shot & 0.38875 & 0.10190 & \cellcolor{green!20}0.7196 & 0.00239 \\ 
        \hline
        Mistral zero-shot & 0.29852 & 0.084103 & 0.5761 & -0.11318 \\ 
        Mistral few-shot & \cellcolor{green!20} 0.31920 & \cellcolor{red!10} 0.065381 & 0.5761 & \cellcolor{green!20} -0.08673 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Comparisons of zero-shot and few-shot results}
\end{center}

@@

@@

>>>>

In the pipeline, topic evolution can be used in two formats. 
The first format allows you to analyze the change of topics in a single dialog. In this format, graphs of changes in the set of topics in the order of the segments will be plotted.

The second format analyzes the entire dataset. 
In this case, either a special mark will be used for timestamp analysis along with each dialog, or the analysis will be performed in the order in which the samples are located in the dataset.

With a large number of topic words, the N most common ones will be selected to visualize their changes.

@@

\begin{center}
    \begin{tabular}{ | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{model} & \multicolumn{1}{| c |}{AMI} &  \multicolumn{1}{| c |}{ICSI} \\
        \hline
        pyannote-speaker-diarization-2.1 & \cellcolor{green!20} 18.9 & 16.4 \\  
        pyannote-speaker-diarization-3.1 & 18.8 & \cellcolor{green!20} 16.7 \\
        whisper + pretrain embeds & \multirow{2}{*}{14.7} & \multirow{2}{*}{13.9} \\
        + agglomerative cluter & & \\
        \hline
    \end{tabular}
    \captionof{table}{Speaker diarization evaluation}
\end{center}

The finished models from pyannote showed better results than the assembled pipeline from whisper and pretraining embeddings. 
Therefore, it was decided to include pyannote models in the final pipeline.

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \cline{2-7}
         & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & 0.446 & 0.458 & 0.378 \\
        TeT + BERT & 0.425 & 0.439 & 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        Our solution+BERT-NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        Our solution+BERT-CLS & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{AMI} & \multicolumn{3}{| c |}{ICSI} \\
        \cline{2-7}
        & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.0641 & 0.762 & 0.730 & 0.109 \\
        GraphSeg & Pk & wd & f1 & Pk & wd & f1 \\
        TextTilling & Pk & wd & f1 & Pk & wd & f1 \\
        TeT + BERT & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        Our solution+BERT-NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        Our solution+BERT-CLS & Pk & wd & f1 & Pk & wd & f1 \\  
        \hline
    \end{tabular}
    \captionof{table}{Dialogue segmentation experiments}
\end{center}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multirow{2}{*}{models} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \cline{2-5}
         & TD & TC & TD & TC  \\ 
        \hline
        LSA  & 0.25824 & 0.00951 & 0.420026 & -0.01929 \\
        BertTopic & 0.34823 & \cellcolor{green!60} 0.02751 & 0.420026 & \cellcolor{green!60} 0.01929 \\
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.80707 & \cellcolor{green!20} 0.01621 & \cellcolor{green!60} 0.49525 & \cellcolor{green!20} 0.005887 \\ 
        Qwen1.5 7B & \cellcolor{green!20} 0.72169  & 0.015453 & \cellcolor{green!20} 0.47777  & -0.07682\\ 
        Mistral 7B & 0.63344 & 0.002248 & 0.34215 & -0.01689 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{2}{| c |}{AMI} &  \multicolumn{2}{| c |}{ICSI} \\
        \cline{2-5}
         & TD & TC & TD & TC  \\ 
        \hline
        LSA & 0.009648 & 0.001375 & 0.013490 & -0.00172 \\ 
        BertTopic & 0.013996 & \cellcolor{green!60} 0.02485 & 0.029090 & \cellcolor{green!60} 0.27210 \\ 
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.50863 & \cellcolor{green!20} 0.11409 & \cellcolor{green!60} 0.76137 & \cellcolor{green!20} 0.14734 \\ 
        Qwen1.5  & \cellcolor{green!20} 0.38641 & 0.10328 & \cellcolor{green!20} 0.7185  & 0.00237\\ 
        Mistral 7B & 0.29852 & 0.084103 & 0.5761 & -0.11318 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Dialogue topics extraction experiments}
\end{center}

The result of experiments in zero-shot that LlaMA 3 8B demonstrate the best performance, it is far ahead of everyone in Topic Diversity and competes in Topic Coherence with BertTopic. 
A strong drawdown in quality relative to extractive model was also noticed in the article PromptTopic \cite{prompttopic:2023}, where the models also lost to BertTopic in Topic Coherence. \\

The main problem at this stage is the problems with the format of the topic words themselves and the formats of the generated output of the model. 
Firstly, the model sometimes gives out not only the word itself but also an explanation of why, there are also options when the model outputs whole sentences or phrases of 3 or more words, which does not suit our task. \\
For example:

\begin{lstlisting}
    good answer for dialogue: 
    car, summer, camp.

    possible bad variants:
    -------------------
    car (because they travel by car)
    summer (because all dialogue about summer)
    camp (because the spent a lot of time in camp)
    -------------------
    we take a car
    spent the whole summer together
    camp was an important place
    -------------------
\end{lstlisting}

Moreover, the zero-shot format has problems with the format of the output generated sequence. 
The model with the same prompt sometimes produces a different format and parsing topic words becomes much more difficult.

\begin{lstlisting}
    possible bad variants:
    -------------------    
    1. car
    2. summer
    3. camp
    -------------------
    * car
    * summer
    * camp
    -------------------
\end{lstlisting}

Consequently, it was important to use different techniques "to embrace" model the correct formats for convenient operation in the whole pipeline.

@@

The few-short approach was explained in the chapter of Methodology.

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{AMI} &  \multicolumn{2}{| c |}{ICSI} \\
        \hline
        model & TD & TC & TD & TC  \\ 
        \hline
        LLaMA3 zero-shot & 0.50863 & 0.11409 & 0.76137 & 0.14734 \\ 
        LLaMA3 few-shot & \cellcolor{green!20} 0.51291 & \cellcolor{green!20} 0.12129 & \cellcolor{green!60} 0.78201 & \cellcolor{red!10} 0.13985 \\ 
        \hline
        Qwen1.5 zero-shot & 0.38641 & 0.10328 & 0.7185 & 0.00237 \\ 
        Qwen1.5 few-shot & 0.38875 & 0.10190 & \cellcolor{green!20}0.7196 & 0.00239 \\ 
        \hline
        Mistral zero-shot & 0.29852 & 0.084103 & 0.5761 & -0.11318 \\ 
        Mistral few-shot & \cellcolor{green!20} 0.31920 & \cellcolor{red!10} 0.065381 & 0.5761 & \cellcolor{green!20} -0.008673 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Comparisons of models in zero-shot and few-shot}
\end{center}

@@

It was also decided to carry out fine-tuning of the models on the selected train part of the datasets (tiage, superseg). 
The main point of this stage is to train the model for a given topic words format and their output format, as in few-shot. 
In addition, it is possible to improve the quality metrics of the models.

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{2}{| c |}{AMI} &  \multicolumn{2}{| c |}{ICSI} \\
        \hline
        model & TD & TC & TD & TC  \\ 
        \hline
        LLaMA3 few-shot & 0.51291 & 0.12129 & 0.78201 & 0.13985 \\ 
        LLaMA3 fine-tuning & \cellcolor{green!30} 0.53812 & \cellcolor{green!20} 0.13329 & \cellcolor{green!20} 0.79854 & \cellcolor{green!30} 0.15636 \\
        \hline
        Qwen1.5 few-shot & 0.38875 & 0.10190 & 0.71960 & 0.00239 \\ 
        Qwen1.5 fine-tuning & \cellcolor{green!30} 0.39471 & \cellcolor{green!20} 0.11004 & \cellcolor{green!20} 0.72041 & 0.00241 \\ 
        \hline
        Mistral few-shot & 0.31920 & 0.065381 & 0.57617 & -0.008673 \\ 
        Mistral fine-tuning & \cellcolor{green!10} 0.31998 & 0.065421 & 0.57531 & \cellcolor{green!50} 0.00031 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Comparisons of models in zero-shot and after fine-tuning}
\end{center}

As with few-shot, the metrics have increased, but now it is convenient to work with the model in the whole pipeline, because now it is easy to understand the "behavior" of the model during response generation.
In addition, the increase in the metric comes from the fact that it was possible to parse all samples, unlike some in zero-shot and few-shot.

@@

In this section, we will show examples of the results of analyzing changes in topics over time.
All examples will be presented on the AMI dataset.

Topic evolution over time on one dialogue:

Topic evolution over time on dataset:
